Plots for Latent Hawkes Paper

### 2021-07-14 output_scripts/Paper_Plots.Rmd
large revamp of paper rmd
remove old plot chunks, update with plots for reponse, etc

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, fig.path = "paper_figure/",
  dev = "png", fig.height = 4.5, fig.width = 7,
  warning = FALSE, cache = TRUE
)

@@

# don't write to this path
data_path <- "../output/"

@@

## New Fig

@@

Plot the negative log of the p values here.

```{r potential-fig3-diag, eval=FALSE}
M1_ks_p <- tibble(ks_p = as.vector(ks_chp), method = "C-HP")

M2_ks_p <- tibble(ks_p = as.vector(ks_dchp), 
                  method = "C-DCHP")

Could repeat this across all cohorts?

What is `data_path` here?

@@

```{r plot-pvalues-m1-m2-here}
ks_p %>% filter(ks_p != 0) %>%
  select(-cols) %>% 
  mutate(id = row_number()) %>% 
  pivot_wider(names_from = method, values_from = ks_p)

bind_cols(M1_ks_p, M2_ks_p) %>% 
  rename(chp_p = ks_p...1, cdchp_p = ks_p...3) %>% 
  filter(chp_p != 0) %>% 
  ggplot(aes(chp_p, cdchp_p)) + geom_point() +
  labs(x = "C-HP p Value", y = "C-DCHP p Value",
       title = "p Value for C-HP and C-DCHP") +
  theme_minimal()

@@

## Figure 3b: Ranking Comparison

```{r fig-3b-rank-comparison, include=FALSE,eval=original_plots}
current_cohort <- 5
colors_plot <- col_df %>%
  filter(method %in% c("C-HP", "C-DCHP")) %>%
  pull(cols)
load(paste(data_path,
  cohort_names[current_cohort],
  "/cohort_hp_stan_result_",
  cohort_names[current_cohort],
  ".RData",
  sep = ""
))
load(paste(data_path,
  cohort_names[current_cohort],
  "/cohort_dchp_stan_result_",
  cohort_names[current_cohort],
  ".RData",
  sep = ""
))
# png(paste(plot_path,"/rank_",cohort_names[current_cohort],".png",sep=''),
#     width=400, height=300)
par(oma = c(0, 0, 2, 0), mar = c(3, 4, 1, 1), mgp = c(0, 0.5, 0))
plot(order(expert_rank_10[[current_cohort]]),
  apply(sim_cohort_hp$f, 2, mean),
  pch = 16, cex = 1.2,
  # col= "steelblue",
  col = colors_plot[1],
  ylab = "", xlab = "",
  xlim = c(1, 12.5), ylim = c(0, 1),
  xaxt = "n", yaxt = "n"
)
segments(order(expert_rank_10[[current_cohort]]),
  apply(sim_cohort_hp$f, 2, mean) -
    apply(sim_cohort_hp$f, 2, sd),
  order(expert_rank_10[[current_cohort]]),
  apply(sim_cohort_hp$f, 2, mean) +
    apply(sim_cohort_hp$f, 2, sd),
  # col= add.alpha("steelblue",0.8),lwd=2)
  col = add.alpha(colors_plot[1], 0.8), lwd = 2
)
points(order(expert_rank_10[[current_cohort]]) + 0.2,
  apply(sim_cohort_dchp$f, 2, mean),
  pch = 16,
  cex = 1.2,
  col = colors_plot[2]
)
# col="goldenrod2")
segments(order(expert_rank_10[[current_cohort]]) + 0.2,
  apply(sim_cohort_dchp$f, 2, mean) - apply(sim_cohort_dchp$f, 2, sd),
  order(expert_rank_10[[current_cohort]]) + 0.2,
  apply(sim_cohort_dchp$f, 2, mean) + apply(sim_cohort_dchp$f, 2, sd),
  col = add.alpha(colors_plot[2], 0.8), lwd = 2
)
# col= add.alpha("goldenrod2",0.8),lwd=2)

axis(BELOW <- 1, at = 1:12, 
     labels = expert_rank_10[[current_cohort]],
     cex.axis = 1.3,
     tck = -0.015)
# mtext(text=11, side=1, line=0.5, cex=1.3, at=6)

axis(LEFT <- 2,
  at = seq(0, 1, 0.2), labels = seq(0, 1, 0.2), las = HORIZONTAL <- 1,
  cex.axis = 1.3, tck = -0.015
)
mtext(side = 1, text = "I&SI rank", line = 1.8, cex = 1.5)
mtext(side = 2, text = "Latent rank", line = 2.4, cex = 1.6)
mtext(side = 3, text = "(b)", line = 0.8, cex = 1.6, font = 2)
legend("bottomleft",
  legend = c("C-HP", "C-DCHP"),
  pch = c(16, 16), lty = c(1, 1), lwd = c(2, 2),
  # col=c("steelblue","goldenrod"),
  col = c(colors_plot[1], colors_plot[2]),
  cex = 1.5
)
# dev.off()
```

```{r, eval=FALSE, include=FALSE}
## need Hmisc for this
library(Hmisc)

par(mar = c(3, 3, 1, 1))
plot(as.vector(n_matrix[n_matrix > 0]),
     as.vector(ks.stat.matrix[n_matrix > 0]),
     xlab = "",
     ylab = "",
     pch = 16,
     col = "gray",
     cex = 0.8,
     xaxt = "n",
     yaxt = "n",
  ylim = c(0, 0.65)
)
mtext("Number of events", cex = 1.5, side = 1, line = 1.8)
mtext("K-S statistics", cex = 1.5, side = 2, line = 1.5)
mgp.axis(1, mgp = c(0, 0.3, 0),
         at = seq(0, 120, 10),
         cex.axis = 1,
         lwd = 0,
         lwd.ticks = 0.1)
mgp.axis(2, mgp = c(0, 0.1, 0),
         at = seq(-0.2, 0.6, 0.2),
         cex.axis = 1,
         lwd = 0,
         lwd.ticks = 0.8)
```

@@

## Figure 4a Recover Latent Ranks
```{r fig-4a, fig.height=3.5, fig.width=8, eval=original_plots}
sim_data_path <- "../output/sims_m3_update/"

# load(paste(sim_data_path,"sim_model3_fit123.RData",sep=''))
# load(paste(sim_data_path,"fit123_state_est.RData",sep=''))
#### need to edit here to account for separate files now

m3_files <- list.files(sim_data_path, pattern = "sim_model3_fit*")
# m1_files

# load(paste0(m1_path,m1_files[1]))
sim_model3_stan_sim1_total <- list()
sim_model3_stan_sim2_total <- list()
sim_model3_stan_sim3_total <- list()

for (i in seq_along(m3_files)) {
  load(paste0(sim_data_path, m3_files[i]))
  sim_model3_stan_sim1_total[[i]] <- sim_model3_stan_sim1
  sim_model3_stan_sim2_total[[i]] <- sim_model3_stan_sim2
  sim_model3_stan_sim3_total[[i]] <- sim_model3_stan_sim3
}

n_sim <- 50

y.ub <- c(12, 12, 12, 12, 12)
text.y <- c(rep(8, 4), 8)
text.x <- c(0.1, 0.2, 0.4, 0.7, 0.9)
text.x.adj <- c(0.3, 0.4, 0.6, 0.5, 0.8)

    ## Posterior density
    # current_result <- eval(parse(text=paste("sim_model3_stan_sim",m,sep="")))
    current_result <- eval(parse(text = paste("sim_model3_stan_sim",
      m,
      "_total",
      sep = ""
    )))
    for (i in c(1:n_sim)) {
      lines(density(current_result[[i]]$f[, j]),
        col = add.alpha(model_colors[m], alpha = 0.8), cex = 0.6, lwd = 0.8
      )
    }

    if (m == 3) {
      text(text.x.adj[j], text.y[j], text.x[j], cex = 2.4)
    }
  }
  ## bottom
  mtext(
    text = expression(f[1], f[2], f[3], f[4], f[5]),
    side = 1, line = 2.4, outer = TRUE,
    at = c(1:length(object_par$f_vec_1)) / length(object_par$f_vec_1) - 0.1,
    cex = 2
  )
  mtext(
    text = "Latent rank variables", side = 1,
    line = 5.3,
    outer = TRUE,
    cex = 2.25,
    at = 0.5
  )
  ## top
  mtext(
    text = "(a)", side = 3,
    line = 0,
    outer = TRUE,
    cex = 2.5,
    at = 0.5, font = 2
  )
  ## left
  mtext(
    text = rev(c("C-HP  ", "C-DCHP", "C-MMHP")),
    side = 2,
    line = 0.5,
    outer = TRUE,
    at = c(0:2) / 3 + 0.15,
    cex = 1.75, las = 2
  )
}
```

```{r fig4a-new-hist, fig.height=3.5, fig.width=8, eval=original_plots}
model_colors <- col_df %>% filter(method %in% c(
  "C-HP",
  "C-DCHP",
  "C-MMHP"
))

m1 <- sim_model3_stan_sim1_total %>%
  map(~ apply(.x$f, 2, mean)) %>%
  enframe() %>%
  unnest(cols = value) %>%
  mutate(
    node_id = rep(c("f1", "f2", "f3", "f4", "f5"), 50),
    method = "C-HP"
  )

m2 <- sim_model3_stan_sim2_total %>%
  map(~ apply(.x$f, 2, mean)) %>%
  enframe() %>%
  unnest(cols = value) %>%
  mutate(
    node_id = rep(c("f1", "f2", "f3", "f4", "f5"), 50),
    method = "C-DCHP"
  )

m3 <- sim_model3_stan_sim3_total %>%
  map(~ apply(.x$f, 2, mean)) %>%
  enframe() %>%
  unnest(cols = value) %>%
  mutate(
    node_id = rep(c("f1", "f2", "f3", "f4", "f5"), 50),
    method = "C-MMHP"
  )

rank_means <- bind_rows(m1, m2, m3)

# rank_means

true_values <- tibble(
  id = c("f1", "f2", "f3", "f4", "f5"),
  values = c(0.1, 0.2, 0.4, 0.7, 0.9),
  val_names = c("   0.1", "0.2", "0.4", "0.7", "0.9")
)

rank_means %>%
  left_join(true_values, by = c("node_id" = "id")) %>%
  ggplot(aes(value, fill = method)) +
  geom_histogram() +
  geom_vline(aes(xintercept = values),
    alpha = 0.6,
    linetype = "dashed"
  ) +
  ### add text here
  geom_text(aes(values, 18, label = val_names),
    size = 3, hjust = 1
  ) +
  scale_fill_manual(values = model_colors) +
  facet_grid(cols = vars(node_id), rows = vars(method)) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
    text = element_text(size = 12),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "none",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  labs(x = "", y = "")
```

@@

```{r new-fig-4a, eval = revision_plots, message=FALSE, warning=FALSE}
sim_data_path <- here("output", "revisions", "sim_m3", "sim_2", "/")

@@

## this is just the mean from each simulation, not the posterior draws

# sim_ranks %>%
#   ggplot(aes(node, rank)) +
#   geom_boxplot() +
#   facet_wrap(~model) +
#   geom_point(data = true_ranks, aes(node, true_rank, colour = "red"),
#              show.legend = FALSE) +
#   labs(title = "All Posterior Draws")
```

@@

To be updated!

```{r data for fig 5,cache=TRUE, eval=revision_plots}
n_sim <- 25

object_par <- list(f_vec_1 = seq(from = 0.1, to = 0.9,
                                 length.out = num_nodes))
### TO DO

@@

## Iteration on 50 simulations
sims <- 1:25
sims <- sims[c(-12, -22, -23, -24)]

@@

```{r fig5a-residual-ks, fig.height=7, eval=original_plots}
# cols_plot <- col_df %>% filter(method %in% c("C-HP","C-DCHP","C-MMHP",
#                                              "True"))

cols_plot <- col_df %>%
  filter(method %in% c(
    "C-HP", "C-DCHP", "C-MMHP",
    "True"
  )) %>%
  arrange(factor(method, levels = c("C-HP", "C-DCHP", "C-MMHP", "True"))) %>%
  pull(cols)
# load("../output/sim_model3_fit123_residuals.RData")
par(mfrow = c(5, 5), mar = c(0.2, 0.2, 0.2, 0.2), oma = c(2.4, 2.4, 2.9, 0.5))
for (i in c(5:1)) {
  for (j in c(5:1)) {
    if (i == j) {
      plot(1, 1,
        type = "n", xlim = c(0, 1), ylim = c(0, 1),
        bty = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n", axes = FALSE
      )
      if (i == 5) {
        polygon(c(0, 0, 0.15, 0.15), c(0.72, 0.8, 0.8, 0.72) + 0.04,
          col = cols_plot[1], border = NA
        )
        polygon(c(0, 0, 0.15, 0.15), c(0.72, 0.8, 0.8, 0.72) + 0.04 - 0.22,
          col = cols_plot[2], border = NA
        )
        polygon(c(0, 0, 0.15, 0.15), c(0.72, 0.8, 0.8, 0.72) + 0.04 - 0.44,
          col = cols_plot[3], border = NA
        )
        polygon(c(0, 0, 0.15, 0.15), c(0.72, 0.8, 0.8, 0.72) + 0.04 - 0.66,
          col = cols_plot[4], border = NA
        )
        text(c(0.43, 0.58, 0.61, 0.4), seq(0.8, 0.14, -0.22),
          c("C-HP", "C-DCHP", "C-MMHP", "True"),
          cex = 1.7
        )
      }
    } else {
      # PR <- c((N_array-Lambda_model1_array)[,i,j],(N_array-Lambda_model2_array)[,i,j],
      #         (N_array-Lambda_model3_array)[,i,j],(N_array-Lambda_true_array)[,i,j])
      PR <- c(
        KS_model1_array[, i, j], KS_model2_array[, i, j],
        KS_model3_array[, i, j], KS_true_array[, i, j]
      )
      ### try pr scores instead
      # PR <- c(PR_model1_array[,i,j],PR_model2_array[,i,j],
      #         PR_model3_array[,i,j],PR_true_array[,i,j])
      Type <- c(rep(1, n_sim), rep(2, n_sim), rep(3, n_sim), rep(4, n_sim))
      boxplot(PR ~ Type,
        col = cols_plot,
        # col = c("steelblue", "goldenrod2", "firebrick2", "chartreuse3"),
        xlab = "", ylab = "", xaxt = "n", yaxt = "n"
      )
      # names = c("C-HP", "C-HP-DC", "C-MMHP", "True")
    }
  }
}
mtext(
  text = c(1:5), side = 2, line = 0.5, outer = TRUE, cex = 2, las = 2,
  at = c(0:4) / 5 + 0.1
)
mtext(
  text = c(5:1), side = 1, line = 1.5, outer = TRUE, cex = 2,
  at = c(0:4) / 5 + 0.1
)
mtext(text = "(a)", side = 3, line = 0.5, outer = TRUE, cex = 2.5, font = 2)
```

New potential Figure 5a plots.

@@

@@

```{r posterior-mean-ranks}
sim_data_path <- here("output", "revisions", "sim_m3", "june_18", "/")

# object_par$f_vec_1

  curr_mean_ranks <- tibble(model = c(rep("C-HP", num_nodes),
                                 rep("C-DCHP", num_nodes),
                                 rep("C-MMHP", num_nodes)),
                       ranks = c(m1_ranks,
                                 m2_ranks,
                                 m3_ranks),
                       node = rep(1:num_nodes, 3),
                       true_rank = rep(object_par$f_vec_1, 3),
                       sim_id = curr_sim)
  sim_ranks_mean <- sim_ranks_mean %>% 
    bind_rows(curr_mean_ranks)

sim_ranks_mean$model <- factor(sim_ranks_mean$model,
                               levels = c("C-HP", "C-DCHP", "C-MMHP"))

sim_ranks_mean %>% 
  # filter(model == "C-MMHP") %>% 
  ggplot(aes(node, ranks, fill = model)) + 
  geom_boxplot() +
  scale_fill_manual(values = cols_plot, guide = 'none') +
  facet_wrap(~model) +
  geom_point(aes(node, true_rank, colour = "True Value"),
             show.legend = TRUE) +
  labs(title = "Mean rank from each simulation") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = "bottom")

@@

no_method <- 4
plot_latent_df <- data.frame(
  Methods = rep(1:no_method, each = 1000 * mice_number),
  Mice = rep(rep(1:mice_number, each = 1000), no_method),
  force = rep(0, 1000 * mice_number * no_method)
)
## agg
plot_latent_df$force[(1:(1000 * mice_number))] <-
  as.vector(sim_agg_rank$x[1001:2000, ])

## M1
plot_latent_df$force[(1:(1000 * mice_number)) +
                       1000 * mice_number] <- as.vector(sim_cohort_hp$f)

## M2
plot_latent_df$force[(1:(1000 * mice_number)) + 
                       2000 * mice_number] <- as.vector(sim_cohort_dchp$f)

## M3
plot_latent_df$force[(1:(1000 * mice_number)) + 
                       3000 * mice_number] <- as.vector(sim_cohort_mmhp$f)

@@

p1 <- ggplot(
  plot_latent_df,
  aes(x = Mice, y = force, fill = Method)) +
  geom_boxplot(alpha = 0.7) +
  scale_fill_manual(values = plot_cols) +
  ggtitle("(a)") +
  theme_bw() +
  theme(
    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
    text = element_text(size = 20),
    axis.text.x = element_text(size = 10),
    legend.position = "none"
  ) +
  facet_grid(cols = vars(Method)) +
  xlab("Mice (ranked by I&SI method)") +
  ylab("Latent rank")
p1
# dev.off()
```

@@

```{r fig-6b-overall-rank-correlation}
load("../output/weighted_rank_data.RData")
# png(paste(plot_path,"real_rank_all_cohort.png",sep=""),width=600,height=300)
no_method <- 4
plot_cor_df <- data.frame(
  Method = rep(c(1:no_method), each = 10),
  cor = as.vector(spearman_df)
)
plot_cor_df$Method <- factor(plot_cor_df$Method,
  labels = c("Agg-rank", "C-HP", "C-DCHP", "C-MMHP")
)
p2 <- ggplot(plot_cor_df, aes(x = "", y = cor, fill = Method)) +
  geom_boxplot(alpha = 0.7, width = 0.5) +
  scale_fill_manual(values = plot_cols) +
  ggtitle("(b)") +
  ylim(0, 1) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
    text = element_text(size = 20),
    axis.text.y = element_text(size = 11),
    legend.position = "none",
    axis.title.x = element_blank()
  ) +
  facet_grid(cols = vars(Method)) +
  ylab("Spearman rank correlation")
p2
```

# Figure 7: Pearson residual matrices

```{r fig-7-prMatrix-Cohort3, fig.width=7, fig.height=7}
current_cohort <- 5
data_path <- "../output/"
## 2 and 8 maybe look better
## 3 probably looks the best

@@

```{r m1-m2-pr, fig.width=6}
current_cohort <- 5
m1_m2_plot <- list(m1_pr[
    rev(expert_rank_10[[current_cohort]]),
    expert_rank_10[[current_cohort]]
  ],
  m2_pr[
    rev(expert_rank_10[[current_cohort]]),
    expert_rank_10[[current_cohort]]
  ])

myMultiMatrixPlot(
  X = m1_m2_plot, no_matrix = 2, n_row = 1,
  xLabels = expert_rank_10[[current_cohort]],
  yLabels = rev(expert_rank_10[[current_cohort]]),
  min = -80, max = 80, axis_cex = 2, title_cex = 1.8,
  colorPalette = "RdBu", if.emp = FALSE,
  # legend.mar=c(0.5,.5,0.5,0.5),
  title_lst = list("C-HP", "C-DCHP"),
  # title_lst = list("I-MMHP"),
  col_axis = c(-80, -40, 0, 40, 80), fake_matrix = TRUE,
  matrix.mar = c(2.5, 2.5, 2.5, 1)
)
```

@@

```{r fig-8a-frob-norm-cohort5, fig.width=8,fig.height=4,eval=TRUE}
load("../output/plot_N_predict.RData")
current_cohort <- 5 # cohort 1 looks worse than rest

@@

p3 <- temp_plot_df %>%
  rowwise() %>%
  # mutate(norm = min(norm,60)) %>%
  # rename(Method = method) %>%
  ggplot(aes(x = method, y = mae, fill = method)) +
  geom_boxplot(alpha = 0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  ggtitle("(a)") +
  theme_bw() +
  theme(
    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
    text = element_text(size = 20),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "right"
  ) +
  facet_grid(cols = vars(day)) +
  xlab("Prediction horizon (day)") +
  ylab("MAE") +
  ylim(0, 8) + # aren't infinite but >150 and <200
  NULL
p3 + labs(fill = "Method", title = "Single Cohort")
```

@@

```{r fig-7a-pred-all-cohorts-box-mae}
### updated to revision
load("../output/plot_N_predict_revision.RData")

@@

@@

```{r fig-glicko-pred-slides,eval=slides_plots,include=slides_plots}
par(mar = c(3, 5, 3, 1))
plot(1,
  type = "n", xlab = "",
  ylab = "Glicko ranking", xlim = c(0, dim(gl$history)[2]),
  ylim = c(min(gl$history[, , 1]), max(gl$history[, , 1])),
  cex.axis = 2, cex.lab = 2
)
for (m in c(1:mice_number)) {
  # history
  lines(gl$history[m, 1:training_end, 1],
    cex = 0.6, col = col_vec[m], lwd = history_width, lty = ltypes_vec[m]
  )
  lines(c(rep(NA, training_end), 
          gl$history[m, (training_end + 1):testing_end, 1]),
    cex = 0.6, col = shade_vec[m], lwd = history_width, lty = ltypes_vec[m]
  )

  # simulation
  cur_end <- testing_end
  mean_vec <- apply(sim_gl_array[m, , ], 1, function(x) mean(na.omit(x)))
  sd_vec <- apply(sim_gl_array[m, , ], 1, function(x) sd(na.omit(x)))
  polygon(c(newx, rev(newx)), c(mean_vec - sd_vec, rev(mean_vec + sd_vec)),
    col = shade_vec[m], border = NA
  )
  # polygon(c(newx), c(mean_vec-sd_vec),col = shade_vec[m], border = NA)
  lines(c(rep(NA, training_end), mean_vec),
    cex = 0.6, col = col_vec[m], lwd = 1, lty = 2
  )
}

# annotate the days
for (d in c(19:21)) {
  abline(v = nrow(df[df$day <= (d - 1), ]), lty = 2, lwd = 0.4)
  text(x = nrow(df[df$day <= (d - 1), ]), y = 2600, d)
}
# mtext(text="(a)", side=3, line=-2.3, outer=TRUE, cex=2.8, at=0.5, font=2)
```

@@

load(paste(data_path, cohort_names[current_cohort],
  "/cmmhp_est_zt_", cohort_names[current_cohort],
  ".RData",
  sep = ""
))
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>%
  group_by(initiator, recipient) %>%
  dplyr::summarize(
    count = n(),
    observe = list(observe.id),
    observe.length = list(observe.time),
    no.events = list(no.events)
  )
unique_observe_win <- unique(return_df[,
                                       c("day", "observe.id", "observe.time")])

@@

## All aggregate
for (t in 1:length(task.types)) {
  temp_vec <- rep(NA, 2000)
  cur_real_rank <- real.gl$history[, day_end_idx[t], 1]
  for (s in c(1:2000)) {
    temp_result <- cor.test(sim_dsnl$x[s, t, ], cur_real_rank,
      method = "spearman"
    )
    temp_vec[s] <- temp_result$estimate
  }
  data.tbl$sub.type[(1:2000) + (t - 1) * 2000] <- sub.types[1]
  data.tbl$task.type[(1:2000) + (t - 1) * 2000] <- task.types[t]
  data.tbl$data.value[(1:2000) + (t - 1) * 2000] <- temp_vec
}

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, fig.path = "paper_figure/revision/",
  dev = "png", fig.height = 4.5, fig.width = 7,
  warning = FALSE, cache = TRUE
)

@@

# don't write to this path
data_path <- "../output/revisions/"

@@

## Test figure (not used)

@@

Plot the negative log of the p values here for all cohorts.

@@

```{r plot-pvalues-m1-m2-here, eval=FALSE}
bind_cols(M1_ks_p, M2_ks_p) %>% 
  rename(chp_p = ks_p...1, cdchp_p = ks_p...3) %>% 
  filter(chp_p != 0) %>% 
  ggplot(aes(chp_p, cdchp_p)) + geom_point() +
  labs(x = "C-HP p Value", y = "C-DCHP p Value",
       title = "p Value for C-HP and C-DCHP") +
  theme_minimal()

@@

## Figure 3b: Residual Structure

```{r fig-3b-residual-structure, include=TRUE, eval=revision_plots}
### now to add Pearson residual matrices here for C-HP and C-DCHP from fig 7
current_cohort <- 5
data_path <- "../output/revisions/"
## 2 and 8 maybe look better
## 3 probably looks the best

matrix_lst_plot <- list(
  m1_pr[
    rev(expert_rank_10[[current_cohort]]),
    expert_rank_10[[current_cohort]]
  ],
  m2_pr[
    rev(expert_rank_10[[current_cohort]]),
    expert_rank_10[[current_cohort]]
  ]
  # ,
  # m3_pr[
  #   rev(expert_rank_10[[current_cohort]]),
  #   expert_rank_10[[current_cohort]]
  # ]
)
# cat("Cohort ",current_cohort,"\n",sep="")
myMultiMatrixPlot(
  X = matrix_lst_plot, no_matrix = 2, n_row = 1,
  xLabels = expert_rank_10[[current_cohort]],
  yLabels = rev(expert_rank_10[[current_cohort]]),
  min = -80, max = 80, axis_cex = 2, title_cex = 1.8,
  colorPalette = "RdBu", if.emp = FALSE,
  # legend.mar=c(0.5,.5,0.5,0.5),
  title_lst = list("C-HP", "C-DCHP", "C-MMHP"),
  # title_lst = list("I-MMHP"),
  col_axis = c(-80, -40, 0, 40, 80), fake_matrix = TRUE,
  matrix.mar = c(2.5, 2.5, 2.5, 1)
)
mtext(text="(b)",side=3,line=0.5,outer=TRUE,cex=2.5,font=2)

## Additional Cohort for Response

Add this below figure to the response to show how different cohorts 
result in different response.

```{r fig3-cohort-response}
current_cohort <- 6

# png(paste(plot_path,"/lambda0_",
# cohort_names[current_cohort],".png",sep=''),
#     width=400, height=300)
matrixPlotParameter(latent_social_matrix[
  rev(expert_rank_10[[current_cohort]]),
  expert_rank_10[[current_cohort]]
],
xLabels = expert_rank_10[[current_cohort]],
yLabels = rev(expert_rank_10[[current_cohort]])
)

@@

@@

```{r fig-4a, eval = revision_plots, message=FALSE, warning=FALSE}
sim_data_path <- here("output", "revisions", "sim_m3", "sim_2", "/")

@@

## this is just the mean from each simulation, not the posterior draws
```

@@

To be updated with the correct paths, etc

```{r data for fig 5,cache=TRUE, eval=revision_plots}
n_sim <- 50
num_nodes <- 10

object_par <- list(f_vec_1 = seq(from = 0.2, to = 0.9,
                                 length.out = num_nodes))

sim_data_path <- here("output", "revisions", "sim_m3", "sim_2", "/")

@@

## Iteration on 50 simulations
sims <- 1:50
sims <- sims[c(-18)]

@@

New potential Figure 5a plots. Need to improve this figure based on the newly
chosen simulation parameters above.

@@

### boxplot of ks statistics
m1_ks <- tibble(Method = "C-HP",
                  ks = as.vector(KS_model1_array[sims, ,]))

m2_ks <- tibble(Method = "C-DCHP",
                  ks = as.vector(KS_model2_array[sims, ,]))

m3_ks <- tibble(Method = "C-MMHP",
                  ks = as.vector(KS_model3_array[sims, ,]))

true_ks <- tibble(Method = "True",
                    ks = as.vector(KS_true_array[sims, ,]))

all_ks <- m1_ks %>% 
  bind_rows(m2_ks) %>% 
  bind_rows(m3_ks) %>% 
  bind_rows(true_ks)

all_ks$Method <- factor(all_ks$Method, levels = c("C-HP",
                                                  "C-DCHP",
                                                  "C-MMHP",
                                                  "True") )

all_ks %>% 
  filter(ks != 0) %>% 
  ggplot(aes(Method, ks, fill = Method)) + 
  geom_boxplot() +
  scale_fill_manual(values = cols_plot) +
  labs(y = "KS Statistic") +
  theme_minimal()

@@

@@

no_method <- 4
plot_latent_df <- data.frame(
  Methods = rep(1:no_method, each = 1000 * mice_number),
  Mice = rep(rep(1:mice_number, each = 1000), no_method),
  force = rep(0, 1000 * mice_number * no_method)
)
## agg
x_draws <- sim_agg_rank %>% select(starts_with("x"))
plot_latent_df$force[(1:(1000 * mice_number))] <-
  as.vector(as.matrix(x_draws))

## M1
f_draws <- sim_cohort_hp %>% select(starts_with("f"))
plot_latent_df$force[(1:(1000 * mice_number)) +
                       1000 * mice_number] <- as.vector(as.matrix(f_draws))

## M2
f_draws <- sim_cohort_dchp %>% select(starts_with("f"))
plot_latent_df$force[(1:(1000 * mice_number)) + 
                       2000 * mice_number] <- as.vector(as.matrix(f_draws))

## M3
f_draws <- sim_cohort_mmhp %>% select(starts_with("f"))
plot_latent_df$force[(1:(1000 * mice_number)) + 
                       3000 * mice_number] <- as.vector(as.matrix(f_draws))

@@

p1 <- ggplot(plot_latent_df, aes(x = Mice, y = force, fill = Method)) +
  geom_boxplot(alpha = 0.7) +
  scale_fill_manual(values = plot_cols) +
  ggtitle("(a)") +
  theme_bw() +
  theme(
    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
    text = element_text(size = 20),
    axis.text.x = element_text(size = 10),
    legend.position = "none"
  ) +
  facet_grid(cols = vars(Method)) +
  xlab("Mice (ranked by I&SI method)") +
  ylab("Latent rank")
p1
# dev.off()
```

@@

```{r fig-6b-overall-rank-correlation}
load("../output/revisions/weighted_rank_data.RData")
# png(paste(plot_path,"real_rank_all_cohort.png",sep=""),width=600,height=300)
no_method <- 4
plot_cor_df <- data.frame(
  Method = rep(c(1:no_method), each = 10),
  cor = as.vector(spearman_df)
)
plot_cor_df$Method <- factor(plot_cor_df$Method,
  labels = c("Agg-rank", "C-HP", "C-DCHP", "C-MMHP")
)
p2 <- ggplot(plot_cor_df, aes(x = "", y = cor, fill = Method)) +
  geom_boxplot(alpha = 0.7, width = 0.5) +
  scale_fill_manual(values = plot_cols) +
  ggtitle("(b)") +
  ylim(0, 1) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
    text = element_text(size = 20),
    axis.text.y = element_text(size = 11),
    legend.position = "none",
    axis.title.x = element_blank()
  ) +
  facet_grid(cols = vars(Method)) +
  ylab("Spearman rank correlation")
p2
```

# Previous Figure 7: Pearson residual matrices

No longer including this figure in the paper

```{r fig-7-prMatrix-Cohort3, fig.width=7, fig.height=7}
current_cohort <- 5
data_path <- "../output/revisions/"
## 2 and 8 maybe look better
## 3 probably looks the best

@@

@@

```{r fig-8a-frob-norm-cohort5, fig.width=8,fig.height=4,eval=TRUE}
load("../output/revisions/plot_N_predict_revision.RData")
current_cohort <- 5 # cohort 1 looks worse than rest

@@

p3 <- temp_plot_df %>%
  rowwise() %>%
  # mutate(norm = min(norm,60)) %>%
  # rename(Method = method) %>%
  ggplot(aes(x = method, y = mae, fill = method)) +
  geom_boxplot(alpha = 0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  ggtitle("(a)") +
  theme_bw() +
  theme(
    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
    text = element_text(size = 20),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "right"
  ) +
  facet_grid(cols = vars(day)) +
  xlab("Prediction horizon (day)") +
  ylab("MAE") +
  ylim(0, 5) + # aren't infinite but >150 and <200
  NULL
p3 + labs(fill = "Method", title = "Single Cohort")
```

@@

```{r fig-7a-pred-all-cohorts-box-mae}
### updated to revision
load("../output/revisions/plot_N_predict_revision.RData")

@@

This has not finished for new simulation setting yet.

@@

@@

load(paste(data_path, cohort_names[current_cohort],
  "/cmmhp_est_zt_", cohort_names[current_cohort],
  ".RData",
  sep = ""
))
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort,
                                    full_data[[cohort_names[current_cohort]]],
                                    clean_data)
unique_pairs_df <- return_df %>%
  group_by(initiator, recipient) %>%
  dplyr::summarize(
    count = n(),
    observe = list(observe.id),
    observe.length = list(observe.time),
    no.events = list(no.events)
  )
unique_observe_win <- unique(return_df[,
                                       c("day", "observe.id", "observe.time")])

@@

dsnl_x_sims <- sim_dsnl %>% select(starts_with("x"))

dsnl_arr <- array(as.matrix(dsnl_x_sims), dim = c(1000, 21, 12))

## All aggregate
for (t in 1:length(task.types)) {
  temp_vec <- rep(NA, 1000)
  cur_real_rank <- real.gl$history[, day_end_idx[t], 1]
  for (s in c(1:1000)) {
    temp_result <- cor.test(dsnl_arr[s, t, ], cur_real_rank,
      method = "spearman"
    )
    temp_vec[s] <- temp_result$estimate
  }
  data.tbl$sub.type[(1:1000) + (t - 1) * 1000] <- sub.types[1]
  data.tbl$task.type[(1:1000) + (t - 1) * 1000] <- task.types[t]
  data.tbl$data.value[(1:1000) + (t - 1) * 1000] <- temp_vec
}

## Utility aggregate
for (t in 1:length(task.types)) {
  temp_vec <- rep(NA, 1000)
  cur_real_rank <- real.gl$history[, day_end_idx[t], 1]
  for (s in c(1:1000)) {
    temp_result <- cor.test(-sim_dsnl_active$x[s, t, ], cur_real_rank,
                            method = "spearman")
    temp_vec[s] <- temp_result$estimate
  }
  data.tbl$sub.type[(1:1000) + (t - 1) * 1000 + 21000] <- sub.types[2]
  data.tbl$task.type[(1:1000) + (t - 1) * 1000 + 21000] <- task.types[t]
  data.tbl$data.value[(1:1000) + (t - 1) * 1000 + 21000] <- temp_vec
}
